Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-09-18 WSSSPE4_report/WSSSPE4_report.tex
adding authors, some assignments

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$, 
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%

@@

@@

@@

\note{need a person to write this - Dan asked Lorraine}

>>>>

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$, 
Sandra Gesing$^{(3)}$, 
Lorraine Hwang$^{(4)}$, 
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ \note{info needed}}

@@

\note{Lorraine and Dan will write this}

@@

\note{Sandra Gesing will write this}

@@

\note{Lorraine will write this}
